A Data-Driven Framework for Neural Field Modelling

### 2010-11-02 ltx/first_order_framework/LaTeX_Manuscript.tex
committing for merge

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.

@@

Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied. For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas. \dean{This is because??? the amplitude the central kernel is low, so noise has a greater effect (although this should just cause a wider confidence interval)?, the amplitude or the outer basis function is high (and the field is too small (boundary issues))? the spatial discretisation stuffs it up (the peaks of the extrema of the continuous kernel do not fall as discrete space locations)?}

>>>>

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(a)), but is missing the higher-frequency detail.

@@

Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied. In all cases the actual kernel fell within the confidence interval of the estimated kernel. The mean kernel estimate for Part b) shows very good accordance with the actual kernel. In the other Parts a) and c) there is an over estimate and an underestimate of the kernel, respectively. These bias are a result
